Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd
caption for fig 9

```{r groups-4and5, fig.cap = "Summary plots for four and five clusters. The distribution of electricity demand combined for all members over $hod$, $moy$, and $wnwd$ is shown. Groups A-1 (customers 21-24), A-2 (customers 4-9), and A-3 (customers 10-15) profiles correspond to Groups B-1, B-2, and B-3, respectively. Cluster A-4 splits into B-4 (customers 16-20) and B-5 (customers 1-3) to produce the five clusters, which better resolves the $moy$ distribution. B-4 is characterized by higher energy consumption in the first few months of the year and more variation in weekend usage. B-5 is distinguished by higher consumption in the middle of the year (winter months) and similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a $moy$ profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals in the group.", fig.height=5}

>>>>

```{r groups-4and5, fig.cap = "Summary plots for four and five clusters showing the distribution of electricity demand combined for all members over $hod$, $moy$, and $wnwd$. Groups A-1 (customers 21-24), A-2 (customers 4-9), and A-3 (customers 10-15) profiles correspond to Groups B-1, B-2, and B-3, respectively. Cluster A-4 splits into B-4 (customers 16-20) and B-5 (customers 1-3) to produce the five clusters, which better resolves the $moy$ distribution. B-4 is characterized by higher energy consumption in the first few months of the year and more variation in weekend usage. B-5 is distinguished by higher consumption in the middle of the year (winter months) and similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a $moy$ profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals in the group.", fig.height=5}
